The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
add keywords
reorder persp

@@

The integration of behavioural and ecological theory has shown the value of
considering the importance of scale to better understand and predict animal
social networks, including demography (Shizuka and Johnson 2019), evolutionary
and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
2017), and animal personality (Sih et al. 2017). While the number of studies
integrating social network theory into a broader array of behavioural and
ecological sub-disciplines is impressive, only recently has the role of animal
space use been been considered in describing the causes and consequences of the
social environment in the context of (1) Individual fitness and phenotypes
(Webber & Vander Wal 2018), (2) habitat selection and space use (He et al.
2019), and (3) movement ecology and collective movement (Bode et al. 2011).
Here, we explore how mutlilayer networks may apply to these emerging fields to
contribute to the development of social network theory and application.

>>>>

## Keywords
Landscape ecology, Movement ecology, Social network analysis, Space use

@@

The integration of behavioural and ecological theory has shown the value of
considering the importance of scale to better understand and predict animal
social networks, including demography (Shizuka and Johnson 2019), evolutionary
and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
2017), and animal personality (Sih et al. 2017). While the number of studies
integrating social network theory into a broader array of behavioural and
ecological sub-disciplines is impressive, only recently has the role of animal
space use been been considered in describing the causes and consequences of the
social environment in the context of (1) Individual fitness and phenotypes
(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode et al. 2011), 
and (3) habitat selection and space use (He et al. 2019).
Here, we explore how mutlilayer networks may apply to these emerging fields to
contribute to the development of social network theory and application.
